JuliaCon Proceedings in Quarto

### 2023-11-16 template.qmd

## Executable Listings  (version $\geq$ 1.4.0)

@@

For example, the following code block will be labeled as `lst-1` and calling `@lst-1` will render as @lst-1. The figure it generates will be labeled as `fig-1` and calling `@fig-1` will render as @fig-1.

```{julia}
#| lst-label: lst-1
#| lst-cap: A listing caption.
#| label: fig-1
#| fig-cap: A figure caption.
#| echo: true

@@

Markdown tables are rendered to LaTeX using the `booktabs` package. This is the recommended way to create tables because it is compatible with various output formats. Tables can be cross-referenced and the table caption will be rendered as a LaTeX table caption. The table generated through the following Markdown syntax is labeled as `tbl-1` and calling `@tbl-1` will render as @tbl-1.

```{.markdown}

@@

>>>>

## Executable Listings  (version $\geq$ 1.4.0) {#sec-executable-listings}

@@

For example, the following code block will be labelled as `lst-1` and calling `@lst-1` will render as @lst-1. The figure it generates will be labelled as `fig-1` and calling `@fig-1` will render as @fig-1.

```{julia}
#| lst-label: lst-1
#| lst-cap: A listing caption.
#| label: fig-1
#| fig-cap: A figure caption.
#| eval: true
#| echo: true

@@

Markdown tables are rendered to LaTeX using the `booktabs` package. This is the recommended way to create tables because it is compatible with various output formats. Tables can be cross-referenced and the table caption will be rendered as a LaTeX table caption.

@@

<!-- | Default | Left | Right | Center |
|---------|:-----|------:|:------:|
| 12      | 12   |    12 |   12   |
| 123     | 123  |   123 |  123   |
| 1       | 1    |     1 |   1    |

: Demonstration of pipe table syntax {#tbl-1} -->

This seems to currently mess with executable listing (@sec-executable-listings).

## LaTeX Tables

Standard LaTeX syntax can also be used to create tables. To use standard Quarto cross-referencing, the LaTeX syntax needs to be wrapped in a `div` with the `tbl` class. The table caption can be added as a paragraph. The following creates @tbl-1 which can be cross-referenced as `@tbl-1`.

```
::: {#tbl-1}

\begin{tabular}{|l|l|}\hline
Age & Frequency \\ \hline
18--25  & 15 \\
26--35  & 33 \\
36--45  & 22 \\ \hline
\end{tabular}

This is a table caption.

:::
```

::: {#tbl-1}

\begin{tabular}{|l|l|}\hline
Age & Frequency \\ \hline
18--25  & 15 \\
26--35  & 33 \\
36--45  & 22 \\ \hline
\end{tabular}

This is a table caption.
